### 2013-12-13 tests_Auto-Mpg.Rmd
added datapoints with 'classic' EPR
ie, no regularization and all monoids are active. This is the closest
version we are able to in accordance to the algorithms from the
references.

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50, lambda=0.8)

@@

save(report, file="Auto-Mpg300.Rda") # recover with load("Auto-Mpg300.Rda")

@@

write.table(df, "Auto-Mpg300.txt")

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, lambda=0.8, runs=25)

@@

save(report, file="Auto-Mpg300_lambda0.8_add_linears.Rda") # recover with load("Auto-Mpg300.Rda")

@@

write.table(df, "Auto-Mpg300_lambda0.8_add_linears.txt")
